{\bf Dynamic Scheduling in Halide}

### 2013-12-17 15869/paper.tex
finish talk and start paper

\section{Introduction}

@@

In this project I investigate and implement {\em dynamic function scheduling}, a new language feature for Halide to support such algorithms.
My approach allows the computations for early pipeline stages to be cached across loop iterations of later stages, so that the results may be reused when data dependencies happen to coincide on the same location.
The principal contribution of this work is the implementation and performance evaluation of {\em dynamic scheduling at pixel granularity}. I also investigated dynamic scheduling at coarser (e.g. tile) granularities, but the problem was more difficult than anticipated; for this I provide some discussion and a design sketch for future work.

\section{Motivation}
% TODO

\section{Design and Interface}
% TODO

\section{Implementation}

@@

\section{Evaluation}
% TODO

\section{Open Questions}
% TODO

\section{Conclusion}
% TODO

\section*{Acknowledgements}

Thanks to Jonathan Ragan-Kelley and Andrew Adams, developers of Halide, for their guidance, insights, and patience. Thanks to Kayvon Fatahalian for supervising this project, and for a great semester in 15-869.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

@@

In this project I investigate and implement {\em dynamic function scheduling}, a new language feature for Halide to support such algorithms.
My approach allows the computations for early pipeline stages to be cached across loop iterations of later stages, so that the results may be reused when data dependencies happen to coincide on the same location, saving redundant computation of a possibly expensive intermediate function.
The principal contribution of this work is the implementation and performance evaluation of {\em dynamic scheduling at pixel granularity}. I also investigated dynamic scheduling at coarser (e.g. tile) granularities, with which entire loop iterations may be skipped. However, the problem was more difficult than anticipated, so I instead provide some discussion and a design sketch for future work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
% TODO

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Design and Interface}
% TODO

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Implementation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation}
% TODO

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Open Questions}
% TODO

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
% TODO

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements}

Thanks to Jonathan Ragan-Kelley and Andrew Adams, developers of Halide, for their guidance, insights, and patience. Thanks to Kayvon Fatahalian for supervising this project and for a great semester in 15-869.
